A Formalization of Complete Discrete Valuation Rings and Local Fields

### 2023-12-11 HAL/CPP_paper_v2.tex
beginning to replace BLABLA

We make an exception to this rule when implementing mixed and equal characteristic local fields, since we do declare \code{valued} instances for them. This creates a mild diamond for $\padicCompl$ and $\FpXCompl$ but this does not cause trouble in our formalization, thanks to the comparison lemma \code{trivial_extension_eq_valuation}\href{https://github.com/LCFT-Lean/local_fields/blob/76ad487d09babdb0018f394a5634526637ee014a/src/discrete_valuation_ring/trivial_extension.lean#L58}{\extlink} mentioned above. Indeed, in all cases where a the inference system would create problems, the lemma allows us to disambiguate the situation: \fil{for an example, we urge the reader to inspect the proof of lemma \code{BLABLA}}.

>>>>

We make an exception to this rule when implementing mixed and equal characteristic local fields, since we do declare \code{valued} instances for them. This creates a mild diamond for $\padicCompl$ and $\FpXCompl$ but this does not cause trouble in our formalization, thanks to the comparison lemma \code{trivial_extension_eq_valuation}\href{https://github.com/LCFT-Lean/local_fields/blob/76ad487d09babdb0018f394a5634526637ee014a/src/discrete_valuation_ring/trivial_extension.lean#L58}{\extlink} mentioned above. Indeed, in all cases where a the inference system would create problems, the lemma allows us to disambiguate the situation: \fil{for an example, we urge the reader to inspect the proof of lemma} \code{FpX_int_completion.equiv_valuation_subring}\href{https://github.com/LCFT-Lean/local_fields/blob/76ad487d09babdb0018f394a5634526637ee014a/src/eq_characteristic/valuation.lean#L97}{\extlink}, \fil{proving that the unit ball inside $\FpXCompl$ as...}.
